Report - Latest Rodent Data

### 2018-12-12 evaluation.Rmd
Switch to portalcasting (#295)
Add portalcasting to package installs, use portalcasting functions to drive directory setup and modeling

* Remove unused tools

* Reorganize, cleanup function writing

* Cleanup website building

* Fix paths for testing

species_of_interest = c('BA','DM','DO','PP','OT','NA','total')
read.csv(
  "https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/Portal_rodent_species.csv",
                          stringsAsFactors = F,na.strings = '') %>%
  dplyr::select(species = speciescode, full_species_name = scientificname) %>%
  dplyr::add_row(species='total', full_species_name='Total Rodents')

>>>>

species_of_interest = c('BA','DM','DO','PP','OT','NA','total')
species_names = read.csv(
  "https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/Portal_rodent_species.csv",
                          stringsAsFactors = F,na.strings = '') %>%
  dplyr::select(species = speciescode, full_species_name = scientificname) %>%
  dplyr::add_row(species='total', full_species_name='Total Rodents')

### 2018-12-12 report.Rmd
Switch to portalcasting (#295)
Add portalcasting to package installs, use portalcasting functions to drive directory setup and modeling

* Remove unused tools

* Reorganize, cleanup function writing

* Cleanup website building

* Fix paths for testing

# get most recent rodent data
observed = portalr::abundance(clean=FALSE, shape='flat', level='treatment', plots='longterm', time = 'newmoon') %>%
            dplyr::filter(newmoonnumber == max(newmoonnumber), treatment=='control')

# get new moon number associated with this period
most_recent_date = read.csv('PortalData/Rodents/moon_dates.csv') %>%
                   dplyr::mutate(censusdate = as.Date(censusdate,format='%Y-%m-%d')) %>%
                   dplyr::filter(newmoonnumber==unique(observed$newmoonnumber)) %>% 
                   dplyr::pull(censusdate)

@@

# get most recent rodent data
observed = portalr::abundance(clean=FALSE, shape='flat', time = 'newmoon') %>%
            dplyr::filter(newmoonnumber == max(newmoonnumber))

# get new moon number associated with this period
most_recent_date = read.csv('PortalData/Rodents/moon_dates.csv') %>%
                   dplyr::mutate(censusdate = as.Date(censusdate,format='%Y-%m-%d')) %>%
                   dplyr::filter(newmoonnumber==unique(observed$newmoonnumber)) %>% 
                   dplyr::pull(censusdate)

>>>>

# get most recent rodent data
observed = portalr::abundance(path = "repo", clean=FALSE, shape='flat', level='treatment', plots='longterm', time = 'newmoon') %>%
            dplyr::filter(newmoonnumber == max(newmoonnumber), treatment=='control')

# get new moon number associated with this period
most_recent_date = read.csv(
  "https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv") %>%
                   dplyr::mutate(censusdate = as.Date(censusdate,format='%Y-%m-%d')) %>%
                   dplyr::filter(newmoonnumber==unique(observed$newmoonnumber)) %>% 
                   dplyr::pull(censusdate)

@@

# get most recent rodent data
observed = portalr::abundance(path = "repo", clean=FALSE, shape='flat', time = 'newmoon') %>%
            dplyr::filter(newmoonnumber == max(newmoonnumber))

# get new moon number associated with this period
most_recent_date = read.csv(
  "https://raw.githubusercontent.com/weecology/PortalData/master/Rodents/moon_dates.csv") %>%
                   dplyr::mutate(censusdate = as.Date(censusdate,format='%Y-%m-%d')) %>%
                   dplyr::filter(newmoonnumber==unique(observed$newmoonnumber)) %>% 
                   dplyr::pull(censusdate)
